Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-28 Paper/MSRChallenge2017.tex
Adding back Tsay and pages of TravisTorrent
changes to the threats to validity

\vspace{1ex}
\noindent\textbf{Metric.} We measured software contribution quality by the
build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to predict build 
success. Decision trees 
use binary decisions on the
attributes to predict a final class. They are well
established and interpretable. We used a WEKA J48 decision tree for readability.
We first built a
decision tree classifier using only technical factors to 
predict build integration
success.  We then included the social factors, to 
identify the degree to which social factors improve the model's predictive
power.
We evaluated the models with 10-fold cross-validation.

@@

Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm.  Without downsampling, the 
decision tree\footnote{decisions trees and datasets: } shows an increase of 4.09\% \textit{correctly classified} instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.

@@

\section{Threats to validity}
\label{sec-threats}

%\paragraph{Internal validity}
We use Weka, a well known machine-learning toolkit,
to analyze our data.
Like all tools, Weka may contain bugs. 
Nonetheless, it is a community tested open source tool, which mitigates threats to 
internal validity. 
We have made our scripts, which analyzed the data sets and
obtained social data publicly available\footnote{https://goo.gl/CqTX44}, for
extension and reproducibility.
We mitigate the risk that our results fail to 
%\paragraph{External validity} 
generalize externally by studying a broad and rich 
 data set~\cite{msr17challenge} comprising 1,359 popular projects.
Similarly, the social factors we study may not apply to closed-source
applications; however, open-source ecosystems are intellectually
valuable sources of study on their own. 
%
 Other concerns include the possibility that social factors
 have changed significantly in the past three years, that unsuccessful
 builds are due to
 incorrect test cases (rather than low quality contributions), and that
 information is lost in collapsing commits' multiple builds. We believe these
 are similarly mitigated by a large and varied data set, but leave investigation
 of the effects of these decisions to future work.

@@

Overall, we conclude that social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction, especially on the downsampled
data. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be
scrutinized as closely as core team member commits before the integration build 
tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build.
Developers with 1000+ followers were more than 10\% more succesful in their
builds compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.

Although experience is an imperfect indicator, 
experienced developers appear more likely to make high quality commits.

>>>>

\vspace{1ex}
\noindent\textbf{Metric.} We measured software contribution quality by the
build status of the
commit. We used a decision tree classifier~\cite{Quinlan86} to predict build 
success. Decision trees 
use binary decisions on the
attributes to predict a final class. They are well
established and interpretable. We used a Weka J48 decision tree for readability.
We first built a
decision tree classifier using only technical factors to 
predict build integration
success.  We then included the social factors, to 
identify the degree to which social factors improve the model's predictive
power.
We evaluated the models with 10-fold cross-validation.

@@

Table~\ref{resultsTable} shows the results of running the two data sets through the
default Weka J48 decision tree algorithm.  Without downsampling, the 
decision tree shows an increase of 4.09\% \textit{correctly classified} instances when adding social data. On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, which outperformed the baseline of
guessing all builds passed (50.00\%).
After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.  These results show that
both technical and social data can be used to improve predictions of build 
integration success.

@@

\section{Threats to Validity}
\label{sec-threats}

%\paragraph{Internal validity}
We have made our scripts, data, and decision tree results publicly 
available\footnote{https://goo.gl/CqTX44}. 
We released these files for
extension, reproducibility, and further investigation of results.
In the study, we use Weka, a well known machine-learning toolkit,
to analyze our data.
Like all tools, Weka may contain bugs. 
Nonetheless, it is a community tested open source tool, which mitigates threats to 
internal validity. 
We mitigate the risk that our results fail to 
%\paragraph{External validity} 
generalize externally by studying a broad and rich 
data set~\cite{msr17challenge} comprising 1,359 popular projects.
Similarly, the social factors we study may not apply to closed-source
applications; however, open-source ecosystems are intellectually
valuable sources of study on their own. 
%
 Other concerns include the possibility that social factors
 have changed significantly in the past three years, that unsuccessful
 builds are due to
 incorrect test cases (rather than low quality contributions), and that
 information is lost in collapsing commits' multiple builds. We believe these
 are similarly mitigated by a large and varied data set, but leave investigation
 of the effects of these decisions to future work.

@@

Overall, we conclude that social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction, especially on the downsampled
data. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be
scrutinized as closely as core team member commits before the integration build 
tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build.
Developers with 1000+ followers were more than 10\% more succesful in their
builds compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.
Although we find experience is an imperfect indicator, 
experienced developers appear more likely to make high quality commits.
